Rigorous Multiple-Precision Evaluation of D-Finite Functions in SageMath

### 2020-03-11 papers/icms2016/main.tex
icms2016: typos (sing → s in two places)

  \tmsession{sage}{default}{\tminput{sage: }{mat =
  diffop.numerical\_transition\_matrix([0, sing[1]], 1e-40)}}

@@

  \tmsession{sage}{default}{\tmunfoldedio{sage:
  }{CBF(-i/(2*sqrt(pi)))*sqrt(sing[1])*(mat[1,2] +
  5*mat[1,3])}{[0.220043767112643 +/- 2.06e-16]}}

>>>>

  \tmsession{sage}{default}{\tminput{sage: }{mat =
  diffop.numerical\_transition\_matrix([0, s[1]], 1e-40)}}

@@

  \tmsession{sage}{default}{\tmunfoldedio{sage:
  }{CBF(-i/(2*sqrt(pi)))*sqrt(s[1])*(mat[1,2] +
  5*mat[1,3])}{[0.220043767112643 +/- 2.06e-16]}}
